Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2024-10-16 paper.tex
Fix typo

\begin{equation}
\label{eq:w_L}
W =
\frac{\partial \phi}{\partial z} =
a_L \omega_L e^{k_L z} \sin{\psi} + \mathcal{O}(\varepsilon_L^4)
\end{equation}
Evaluating these velocities at the wave surface $z = \eta_L$ rather than at
the mean water level $z=0$ is a departure from the linear theory, making the
treatment of the long waves here as weakly nonlinear.
As \citet{zhang1990evolution} point out, this is appropriate to do when the
amplitude of the long waves is of the similar magnitude or large than the
wavelength of the short waves.

>>>>

\begin{equation}
\label{eq:w_L}
W =
\frac{\partial \phi}{\partial z} =
a_L \omega_L e^{k_L z} \sin{\psi} + \mathcal{O}(\varepsilon_L^4)
\end{equation}
Evaluating these velocities at the wave surface $z = \eta_L$ rather than at
the mean water level $z=0$ is a departure from the linear theory, making the
treatment of the long waves here as weakly nonlinear.
As \citet{zhang1990evolution} point out, this is appropriate to do when the
amplitude of the long waves is of the similar magnitude or larger than the
wavelength of the short waves.
